\bigskip GRASS GIS Vector State of the Art - Gearing towards GRASS GIS 7 \bigskip

### 2014-04-16 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape poster: ref fix
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59699 15284696-431f-4ddb-bdfa-cd5b030d7da7
2014_EGU_G7_Landscape: standard box for references and PyGRASS and TGRASS added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59747 15284696-431f-4ddb-bdfa-cd5b030d7da7

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
% \scriptsize <<- too small for a poster!
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1): 51-61.\\{}
[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

>>>>

% \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{ % special smaller box
\blocknode{References}{
% \scriptsize <<- too small for a poster!
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
[3] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
[5] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}
